---
title: "How to use `prepend_current_date`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use `prepend_current_date`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(ojoutils)
```

# Introduction

The `prepend_current_date` function provides a convenient way to add the current date to a file name. This can be useful for versioning files or keeping track of when files were created or modified.

This vignette demonstrates how to use the `prepend_current_date` function in various scenarios, including basic usage and handling different input formats.

# Basic Usage

To add the current date to a file name, you can call `prepend_current_date` with the file name as an argument. For example:

```{r}
# Adding the current date to a file name
prepend_current_date("data/output/parties.csv")
```

In this example, if today's date were 2025-03-17, the output would be:

```
"data/output/2025_03_17_parties.csv"
```

# Handling Different Input Formats

The `prepend_current_date` function is designed to handle different input formats as specified in the issue. Here are some examples:

## Example 1: Using `here` package

```{r}
# Using here package with prepend_current_date
write_csv(parties, here::here(prepend_current_date("data/output/parties.csv")))
```

## Example 2: Nested `prepend_current_date` inside `here`

```{r}
# Nested prepend_current_date inside here
write_csv(parties, prepend_current_date(here::here("data/output/parties.csv")))
```

## Example 3: Combining `here` and `prepend_current_date`

```{r}
# Combining here and prepend_current_date
write_csv(parties, here::here("data/output/", prepend_current_date("parties.csv")))
```

# Using the `append` Argument

The `prepend_current_date` function also provides an `append` argument that allows you to append the current date to the file name instead of prepending it. Here are some examples:

## Example 1: Appending the Date

```{r}
# Appending the current date to a file name
prepend_current_date("data/output/parties.csv", append = TRUE)
```

In this example, if today's date were 2025-03-17, the output would be:

```
"data/output/parties_2025_03_17.csv"
```

## Example 2: Using `here` package with `append`

```{r}
# Using here package with prepend_current_date and append
write_csv(parties, here::here(prepend_current_date("data/output/parties.csv", append = TRUE)))
```

## Example 3: Nested `prepend_current_date` with `append` inside `here`

```{r}
# Nested prepend_current_date with append inside here
write_csv(parties, prepend_current_date(here::here("data/output/parties.csv"), append = TRUE))
```

# Conclusion

The `prepend_current_date` function is a simple yet powerful tool for adding the current date to file names. It helps in organizing and versioning files effectively. By handling different input formats and providing the `append` argument, it offers flexibility in various scenarios.

For more advanced usage and customization, refer to the function's documentation and examples.
