---
title: "How to use `stamp_date`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use `stamp_date`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(ojoutils)
```

# Introduction

The `stamp_date` function provides a convenient way to add the current date to a file name. This can be useful for versioning files or keeping track of when files were created or modified.

This vignette demonstrates how to use the `stamp_date` function in various scenarios, including basic usage and handling different input formats.

# Basic Usage

To add the current date to a file name, you can call `stamp_date` with the file name as an argument. For example:

```{r}
# Adding the current date to a file name
stamp_date("data/output/parties.csv")
```

In this example, if today's date were 2025-03-17, the output would be:

```
"data/output/2025_03_17_parties.csv"
```

# Handling Different Input Formats

The `stamp_date` function is designed to handle different input formats as specified in the issue. Here are some examples:

## Example 1: Using `here` package

```{r}
# Using here package with stamp_date
readr::write_csv(parties, here::here(stamp_date("data/output/parties.csv")))
```

## Example 2: Nested `stamp_date` inside `here`

```{r}
# Nested stamp_date inside here
readr::write_csv(parties, stamp_date(here::here("data/output/parties.csv")))
```

## Example 3: Combining `here` and `stamp_date`

```{r}
# Combining here and stamp_date
readr::write_csv(parties, here::here("data/output/", stamp_date("parties.csv")))
```

# Conclusion

The `stamp_date` function is a simple yet powerful tool for adding the current date to file names. It helps in organizing and versioning files effectively. By handling different input formats, it provides flexibility in various scenarios.

For more advanced usage and customization, refer to the function's documentation and examples.
